Software Citation Principles

### 2016-03-17 sc-principles/software-citation-principles.tex
fixed some unintentional bullets in table 2

Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\

@@

Indexer                     & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet \\
Domain group           & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\
Library\slash archive & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\

>>>>

Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\

@@

Indexer                     & build catalog of software               & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &            & \textbullet \\
Domain group           & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
Library\slash archive  & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
